Predicting Sales Level for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-29 paper.tex
improving some sentences in the abstract

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%First you have to explain why it is enough to predict the level of
%sales, and not the precise number. 
% Antonio - it is true, but how can we justify this, JJ?
% I guess that precision is relative in this kind of methods, since the publisher is not going to print exactly '237' books due to it is the output of a regression method. Instead, there could be a range of books to be printed (as a standard) related with an expected 'low', 'medium', 'high' or 'very high' amount of sales.
% Moreover, I guess that the classification output, considering four classes would work better (more precisely and close to reality) than regression.
% What do you think?
An important task when publishing a new book is determining the number 
of copies to be printed, since doing both a (dramatic) under- or overestimation will lead to important financial losses.
In this paper, we transform this problem into a classification one, defining different sales levels i.e. classes. The obtained results will be easier to interpret by publishers than other black-box techniques, so they will consider them in their decision process.
The problem of predicting these levels has been addressed applying cost-sensitive ensemble methods.
% Antonio - explain briefly what are them
These can be used as reliable decision-aid tools for publishers, as a part of the final stages of the editorial process. 
Thus, a real dataset including the complete sales data for books published in Spain across several years has been used to compute the prediction models.
% Antonio - extend a bit this with the followed methodology.
% Explain also the method you are using and why it's an improvement
% over the previous one - JJ
We evaluate our approach on the real data collected by a Spanish publishing company.
Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%First you have to explain why it is enough to predict the level of
%sales, and not the precise number. 
% Antonio - it is true, but how can we justify this, JJ?
% I guess that precision is relative in this kind of methods, since the publisher is not going to print exactly '237' books due to it is the output of a regression method. Instead, there could be a range of books to be printed (as a standard) related with an expected 'low', 'medium', 'high' or 'very high' amount of sales.
% Moreover, I guess that the classification output, considering four classes would work better (more precisely and close to reality) than regression.
% What do you think?
An important task when publishing a new book is determining the number 
of copies to be printed, since doing both a (dramatic) under- or overestimation will lead to important financial losses.
In this paper, we transform this problem into a classification one, defining different sales levels i.e. classes. 
The obtained results will be easier to interpret by publishers than other black-box techniques, 
so these methods can be used as reliable decision-aid tools for publishers, to be considered in their decision as a part of the final stages of the editorial process.

The problem of predicting these levels has been addressed applying cost-sensitive ensemble methods.
% Antonio - explain briefly what are them  and  the followed methodology.
In order to do so, a real dataset collected by a Spanish publishing company, including the complete sales data for books published in Spain across several years, has been used to design and evaluate the prediction models.
% Explain also the method you are using and why it's an improvement over the previous one - JJ
Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.
